Acoustic forcing of a laminar viscous jet through a circular aperture in a thick plate : Impedance calculations and instability criteria

### 2018-10-09 DEVELOPMENT_CASES/WhistlingHole/JFM_PartII_Draft/thick_hole_2018.tex
New draft of part II on Whistling holes !!!

The problem of Rayleigh was reconsidered by Howe, in presence of a base flow, leading to a prediction for the conductivity as function of the Strouhal number. The derivation is extremely technical and not reproduced here. The final result amounts to :
$$
K = 2R ( \gamma - i \delta)
$$
with
\be
\gamma = \frac{
I_1(\Omega^*)^2[1+1/\Omega^*]+(4/\pi^2) e^{2\Omega^*}\cosh(\Omega^*) K_1(\Omega^*)^2[\cosh(\Omega^*)-\sinh(\Omega^*)/\Omega^*]
}
{
I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
}
\label{eq:gammaHowe}
\ee

\be
\delta = 
\frac{
(2/\pi \Omega^*) I_1(\Omega^*) K_1(\Omega^*)e^{2\Omega^*}
}
{
I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
}
\label{eq:deltaHowe}
\ee

Note that in the calculation of Howe, the Strouhal number is defined as $\Omega^* = \omega R/U$ where $U$ is the velocity of convection of the vorticity along the vortex sheet. Howe argues that $U= U_J/2$, in accordance with the classical modeling of the Kelvin-Helmholtz instability.
Hence the relationship with the Strouhal number used in the present paper is $\Omega^* = \Omega/(2 \alpha)$, and the two definitions are equivalent if $\alpha = 1/2$.

@@

@@

\section{The viscous problem : analysis and numerical method}

@@

\subsection{Upstream domain}

@@

The treatment of the outlet conditions is a delicate point here, as the structure of both the base flow and the perturbation lead to some difficulties, especially when the Reynolds number becomes large. These difficulties led us to use an original method which consists of using a change of variables from a computational domain defined with $[X,R]$ coordinates to the physical domain with $[x,r]$ coordinates.

The first motivation for this method comes from the structure of the base flow. In effect, the laminar, steady solution 
 $[u_0,p_0]$ is characterized by a boundary layer which remains very sharp at large distances from the hole. More specifically, the boundary layer thickness $\delta$ scales as  $\delta(x) \approx \sqrt{\nu x/U_J}\approx Re^{-1/2} x^{1/2}$. Of course, in a real, High-Reynolds jet, the boundary layer thickness grows much faster because of turbulence. However, the global method used here requires computation of a laminar base flow  so we have to work around this issue. The solution is to use a change of coordinates $x = G_x(X)$ which stretches the outer domain from $X\in [0,X_{max}]$ to $[0,x_{max}]$, where the bound of the computational $X_{max}$ is relatively small, while the corresponding $x_{max} = x(X_{max})$ is several orders of magnitude larger.

The second issue is due to the structure of the perturbation. In effect, the jet is spatially unstable, and thus perturbations are convectively amplified in the downstream perturbation, and far away from the hole, they reach levels several orders of magnitude larger than the levels in the vicinity of the hole. As soon as the ratio between minimum and maximum levels of the perturbation becomes of the order of the numerical round-off error 
($10^{-15}$ using double-precision) this issue leads to the impossibility to compute accurately the structure of the perturbation in the vicinity of the whole, which is mostly relevant for the computation of the conductivity. In practice, when solving the problem in terms of the physical coordinates, this issue limits the validity of the results to $Re \leq 800$.

To detail the origin of the problem and introduce the idea used to overcome it, let us review the classical modeling of the Kelvin-Helmholtz instability for a planar shear layer of zero thickness in the inviscid case. The derivation can be found in any classical textbook on hydrodynamical stability (e.g. Shandrasekar, Drazin \& Reid, Charru, etc..). 
Consider as a base flow a shear layer separating two regions of constant axial velocity, namely $u= U$ for $y<0$ and $u=0$ for $y>0$. Now assume that the perturbation consists of a displacement of the shear layer with the form
\be 
y = \eta \approx e^{i k x - i\omega t} 
\label{eq:etaKH}
\ee
and assume a similar modal expansion for the velocity potential in the upper and lower region. Matching the two regions at the interface leads to the classical dispersion relation :
\be 
c \equiv \frac{\omega}{k} = \frac{1+i}{2} U
\label{eq:cKH}
\ee 
In a temporal stability framework, this means that a perturbation with real wavenumber $k$ will be convected
downstream with a phase velocity $U/2$ and temporally amplified with a growth rate $U k/2$. On the other hand, in a spatial stability framework ($\omega$ real, $k$ complex), which is more relevant here, this means that any perturbation will be spatially amplified downstream and will diverge at $x\rightarrow +\infty$. This divergence forbids a global resolution of the function $\eta(x,t)$ when the spatial variable $x$ is {\em real}. However, the problem disappears if we consider an analytical continuation of the function $\eta(x,t)$ with a {\em complex variable} $x$. More specifically, as $\arg(k) = -\pi/4$, the function $\eta(x,t)$ becomes convergent as soon as $|x| \rightarrow \infty$ in a direction of the complex plane verifying $\pi/4 < \arg(x) 5\pi/4$.

Thus, this study of the simple, inviscid, planar shear layer suggests a possible way to resolve the problem for the present case of a viscous, cylindrical shear layer : using a { \em  complex coordinate change} which maps the numerical $X \in [0;X_{max}]$ (with $X$ real) into a path for the physical $x$ coordinate which enters the complex plane and follows a direction where the perturbation is spatially damped.

@@

\be
\begin{array}{rcll}
x = G_x(X) &=& \frac{X}{\left[1-X^2/L_s^2 \right]^2} \left[ 1 + i \gamma_c \tanh \left(\frac{X}{L_c}\right)^2  \right]  & \mbox{ for } X>0, \\
	& = & X & \mbox{ for } X<0.
\end{array}
\label{eq:mapX}
\ee
This choice has the following properties. First, it leaves the axial coordinate unchanged in the upstream domain and inside the hole $(x<0)$. Secondly, the numerical and spatial coordinates are also almost identical in the region where the jet emerges from the hole (namely  $x \leq L_c$ and $x \leq L_s$). Thirdly, as $X$ approaches the upper bound of the numerical domain $X_{max}$, and complex, the 
physical variable tends to $x_{max}= G_x(X_{max}$, which is very large as soon as $L_c$ is close to $X_{max}$
(with $L_s > X_{max}$), and complex, with argument $\tan^{-1} (\gamma_c)$, as soon as $\gamma_c \neq 0$.

@@

This function leaves the radial coordinate unchanged in the upstream domain an in the region $r<R_{s1}$ where the jet develops, but it stretches the limit of the domain from $R_{max}$ to $r_{max} = G_r(R_{max})$ which is very
large as soon as $R_{s2}$ is close to $R_{max}$ (with $r_{s2} > R_{max}$).

Having explained this change of coordinates, it remains to specify the boundary conditions to be used at the outer limits of the computational domain. For the resolution of the Navier-Stokes equation in an open domain, the physically relevant boundary condition $[{\bf u}; p] \rightarrow [0; p_{out}]$ as $(x,r) \rightarrow \infty$   
are often replaced by setting the traction (or pseudo-stress) $-p {\bf n} + \nu \nabla {\bf u} \cdot {\bf n} $ to zero
at the outlet boundaries. An alternative choice is to nullify the stress $-p {\bf n} + \nu ( \nabla {\bf u} + \nabla {\bf u}^T) \cdot {\bf n} $. In the present case, we have chosen to impose a zero-traction condition at the boundaries $x_{max},r_{max}$, for both the base flow and the perturbation. A zero-stress condition was also tried, leading to similar results but convergence difficulties when computing the base flow. Note that the significance of

Note that the use of complex coordinate mapping for linear problems involving a single spatial coordinate is customary in stability studies, and mathematical theorems are available to justify how to chose the integration contour as function of the singularities of the problem (e.g. Bender \& Orzag). On the other hand, its use for a nonlinear problem (i.e. computation of the base flow) involving two spatial coordinates is totally new to our knowledge. The validity of the method is not justified by rigourous mathematical argument, but only by the fact that it effectively works and that the results are independent upon the parameters of the mapping. A few test showing that it is effectively the case, for both the base flow and the perturbation, are given in appendix A.

@@

\begin{figure}
$$
\includegraphics[width = .8 \linewidth]{FIGURES/Mesh.eps}
$$
\caption{Example of computational mesh with dimensions in mapped coordinates and nomenclature of boundaries.} 
\label{fig:Mesh}
\end{figure}

The numerical resolution of the problem was performed with a finite element method,  using the FreeFem++ software. An example of computational mesh, in the $[X,R]$ coordinates, is shown in figure 2. Meshes were generated using Delaunay-Voronoi triangulation of the domain, and subsequently refined locally to fit the steep gradients of both the base flow and the perturbation using the adaptmesh command provided by the Freefem++ software.

For resolution, the Navier-Stokes equations have first to be expressed in terms of the mapped coordinates. For this purpose, the spatial derivatives have to be modified as follows :

\be
\DP{}{x} \equiv H_x \DP{}{X}  \quad \mbox{ with } H_x =   \frac{1}{G_x'};
\ee
\be
\DP{}{r} \equiv H_r \DP{}{R}  \quad \mbox{ with } H_r =   \frac{1}{G_r'}.
\ee

The incompressible Navier-Stokes operator thus have the following form :

\be
{\cal NS} \left[\begin{array}{c} u_x \\ u_r  \\ p \end{array} \right] =
 \left[\begin{array}{c}
- (u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x) - H_x \partial_X p 
+ \nu \left[ H_x \partial_X ( H_x \partial_X u_x ) + H_r/r\partial_R ( r H_r \partial_r u_x ) \right]
\\
- (u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r) - H_r \partial_R p 
+ \nu \left[ H_x \partial_X ( H_x \partial_X u_r ) - u_r/r^2 + H_r/r\partial_R ( r H_r \partial_r u_r ) \right]
\\
H_x \partial_X u_x + H_r/r \partial_R (r u_r) 
\end{array} \right] 
\label{eq:NS}
\ee

to solve these equations using finite element method, we classically multiply by test functions 
$[u_x^*, u_r^*,p^*]$ and integrate over the domain. Note that this integration has to be done over the physical domain, so in terms of the numerical variables the elementary volume of integration is $dV = r dr dx = (H_x H_r)^{-1} r dR dX$ .
After integration by parts of the pressure gradient and Laplacian terms, we are thus lead to the following weak formulation:

\be
\begin{array}{l}
\displaystyle
- \int \left[ 
u_x^* \left( u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x \right) 
+ u_r^* \left( u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r \right) 
\right] dV
\\
\displaystyle
+ \int \left[ 
p \left( H_x \partial_X u_x^* + H_r \partial_R u_r^* + u_r^*/r \right) 
-
p^* \left( H_x \partial_X u_x + H_r \partial_R u_r + u_r/r \right) 
\right] dV
\\
\displaystyle
- \int \left[ 
H_x^2 \partial_X u_x \partial_X u_x^* +H_r^2 \partial_R u_x \partial_R u_x^*
\right] dV
\\
\displaystyle
- \int \left[ 
H_x^2 \partial_X u_r \partial_X u_r^* +H_r^2 \partial_R u_r \partial_R u_r^*
+ u_r u_r^*/r^2
\right] dV
\\
= 0.
\end{array}
\ee

Note that with this formulation, the no-traction boundary conditions at the outlet boundary, as well as the symmetry condition at the axis and the zero tangential stress condition at the lateral wall of the cavity are automatically satisfied thanks to the integration by parts. The other boundary conditions are imposed by penalization.

Following a now customary approach, the computation of the base flow is done using a standart Newton method. The algorithm is as follows :
\begin{description}
\item[$(i)$] Start from a guess flow field $[{\bf u}^g;p^g]$.
\item[$(ii)$] Solve the linear system ${\cal NS}[{\bf u}^g,p^g] + {\cal L}_g [\delta {\bf u}, \delta p]$ where $ {\cal L}_g$ is the linearized Navier-Stokes operator around the guess field.
\item[$(iii)$] Obtain a better guess as $ [{\bf u},p] = [{\bf u}^g,p^g] +  [\delta {\bf u}, \delta p]$.
\item[$(iv)$] Repeat until convergence.
\end{description}
The inversion at step $(ii)$ is done with the UMFPACK64 library.

In practice, at point $(i)$ the guess field is generally taken as the base flow computed at a lower value of the Reynolds number. The whole algorithm is thus repeated for increasing values of the Reynolds number to generate a family of base flow. The mesh refinement is applied at each step, so that the refinement, and the number of points of the mesh, increases with the Reynolds number. Note that when using the complex mapping method described above, the radius of convergence of the Newton algorithm seems to be smaller than in the standard case.  This means that the Reynolds number has to be increased moderately between successive base flow computations.

The computation of the perturbations due to harmonic forcing $[u_x',u_r',p']$ is done using the same linear solver UMFPACK64. Note that the structure may involve steeper gradients compared to the base flow. To capture this, the problem is first solved on the refined mesh computed during the base flow computation. The mesh is subsequently refined a second time through the adaptmesh command, and the base flow and the perturbation are finally recomputed on this better mesh.

@@

\section{The nonzero thickness case}

@@

\subsection{Base flows : study of the recirculation region}

@@

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Recirculation.eps}
$$
\caption{ Intensity of the recirculation flow inside the hole as function of $Re$, 
for $\beta = 0.1$ (dots),  $0.3$ (dashes),  and $1$ (long dashes). }
\label{fig:Umax}
\end{figure}

@@

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Alpha_VennaContracta.eps}
$$
\caption{ Vena contracta coefficient as function of $Re$, for $H_h/D_h = 0$ (full line), 
 $H_h/D_h = 0.1$ (dots),  $H_h/D_h = 0.3$ (dashes),  $H_h/D_h = 1$ (long dashes). }
\label{fig:alpha}
\end{figure}

@@

%\clearpage
\subsection{Unsteady flow}

\subsubsection{Case $\beta = 0.3$}

@@

\begin{figure}
$$
\includegraphics[width=.8\linewidth]{FIGURES/Ep03_RL.eps}
$$
\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
for a hole of thickness $\beta = 0.3$, for %$Re = 100$ ($\cdot \cdot \cdot$), 
$Re = 500$ (-- --, black),
$Re = 800$ (-- $\cdot$ --, red ),  $Re = 1500$ (---  ---, green),  and
$Re = 3000$ (--- $\cdot$ ---, blue). 
%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.
}
\label{fig:Cond03}
\end{figure}

@@

\subsubsection{Case $\beta = 1$}

@@

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.8\linewidth]{FIGURES/Ep1_RL.eps}
\end{array}
$$
\caption{ 
$(a)$ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance for a hole of thickness
$\beta = 1$, for $Re = 800$ (--$\cdot$--, red), $Re = 1200$ ( --$ \cdot \cdot$--, magenta) and $Re = 1500$ (---  ---, green).
}
\label{fig:Cond1}
\end{figure}

@@

@@

\subsubsection{Case $\beta = 0.1$}

@@

\subsubsection{Case of a rounded hole}

@@

\section{Parametric study}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Re.eps}
$$
\caption{ Thresholds for the onset of acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
}
\label{fig:ThresholdsRe}
\end{figure}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Om.eps}
$$
\caption{ Frequencies corresponding to acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
}
\label{fig:ThresholdsRe}
\end{figure}

@@

\appendix
\section{Numerical validations}
Only the mesh and mayle the parameter $L_M$

>>>>

@@

WE HAVE TO EXPLAIN THE TWO CRITERIA

1/ Acoustic instability

$Z_r(\omega)$ < 0 for some real $\omega$

Demonstrate that in this case, we have over reflexion.

2/ Hydrodynamic instability.

$Z_r>0$ and $Z_I>0$ for some real $\omega$

FIGURE : sketch showing the NYQUIST diagrams.

REWRITE IN TERMS OF IMPEDANCE

@@

\section{Numerical method}

\includegraphics[width=.6\linewidth]{fig/mesh.eps}

@@

THE REMAINDER IS THE SAME AS IN PART I.

SPECIFY THAT THE PROGRAM IS AVAILABLE ONLINE AS PART OF THE STABFEM PROJETCT.

@@

MAYBE EVERYTHING ABOUT COMPLEX MAPPING SHOULD BE POSTPONED IN APPENDIX ???

@@

\be
\begin{array}{rcll}
x = G_x(X) &=& \frac{X}{\left[1-(X-X_{s1}^2/(L_s-X_{s1})^2 \right]^2} \left[ 1 + i \gamma_c \tanh \left(\frac{X-X_{s1}}{L_c}\right)^2  \right]  & \mbox{ for } X>0, \\
	& = & X & \mbox{ for } X<0.
\end{array}
\label{eq:mapX}
\ee

This choice has the following properties. First, it leaves the axial coordinate unchanged in the upstream domain and inside the hole,
AND IN THE DOWNSTREAM REGION UP TO $(x<X_{s1})$
. Secondly, the numerical and spatial coordinates are also almost identical in the region where the jet emerges from the hole (namely  $x \leq L_c$ and $x \leq L_s$). Thirdly, as $X$ approaches the upper bound of the numerical domain $X_{max}$, and complex, the 
physical variable tends to $x_{max}= G_x(X_{max}$, which is very large as soon as $L_c$ is close to $X_{max}$
(with $L_s > X_{max}$), and complex, with argument $\tan^{-1} (\gamma_c)$, as soon as $\gamma_c \neq 0$.

@@

@@

SEE STABFEM AND PART I.

We should explain the two kibnds of problems:

1/ Forced harmonic problem => imepedance

2/ Eigenvalue problem

@@

%\section{The nonzero thickness case}

\clearpage

\section{Base flows : study of the recirculation region}

@@

@@

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{fig/Umin.eps}
$$
\caption{ Intensity of the recirculation flow inside the hole as function of $Re$, 
for $\beta = 0.1$ (dots),  $0.3$ (dashes),  and $1$ (long dashes). }
\label{fig:Umax}
\end{figure}

@@

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{fig/Vena_contracta.eps}
$$
\caption{ Vena contracta coefficient as function of $Re$, for $H_h/D_h = 0$ (full line), 
 $H_h/D_h = 0.1$ (dots),  $H_h/D_h = 0.3$ (dashes),  $H_h/D_h = 1$ (long dashes). }
\label{fig:alpha}
\end{figure}

@@

SUGGESTION ABOUT USAGE OF COMPLEX MAPPING AND FIGURE MANAGEMENT.

I SUGGEST TO USE A COMPLEX MAPPING WITH $X_s=3 (or 5)$

IN THE WHOLE PAPER WE SHOULD ONLY PLOT THE STRUCTURES (and sensitivity) IN THE REGION NOT AFFECTED BY MAPPING.

APPENDIX : STRUCTURE USING COMPLEX MAPPING.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
\section{Linear results for FORCED PROBLEM}

\subsection{Case $\beta = 0.3$}

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re800_EP03.eps}
&
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1000_EP03.eps}
\\
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1200_EP03.eps}
&
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1600_EP03.eps}
\\
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re2000_EP03.eps}&
\end{array}
$$
\caption{Nyquist diagrams for $\beta = 0.3$. CHECK THE FIGURES !!!!}
\end{figure}

@@

%ig/Vena_contracta.eps
%\begin{figure}
%$$
%\includegraphics[width=.8\linewidth]{FIGURES/Ep03_RL.eps}
%$$
%\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
%for a hole of thickness $\beta = 0.3$, for %$Re = 100$ ($\cdot \cdot \cdot$), 
%$Re = 500$ (-- --, black),
%$Re = 800$ (-- $\cdot$ --, red ),  $Re = 1500$ (---  ---, green),  and
%$Re = 3000$ (--- $\cdot$ ---, blue). 
%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.
%}
%\label{fig:Cond03}
%\end{figure}

@@

%\begin{figure}
%\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_1_33.eps}

\subsection{Case $\beta = 1$}

@@

%\begin{figure}
%$$
%\begin{array}{cc}
%\includegraphics[width=.8\linewidth]{FIGURES/Ep1_RL.eps}
%\end{array}
%$$
%\caption{ 
%$(a)$ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance for a hole of thickness
%$\beta = 1$, for $Re = 800$ (--$\cdot$--, red), $Re = 1200$ ( --$ \cdot \cdot$--, magenta) and $Re = 1500$ (---  ---, green).
%}
%\label{fig:Cond1}
%\end{figure}

@@

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re800_EP1.eps}&
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1200_EP1.eps}\\
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1600_EP1.eps}&
\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re2000_EP1.eps}
\end{array}
$$
\caption{Nyquist diagrams for $\beta = 1$. CHECK THE FIGURES !}
\end{figure}

@@

\subsection{Case $\beta = 0.1$}

IS IT USEFUL TOI KEEP THIS ????

@@

\clearpage

\subsection{Parametric study}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{fig/Re_beta.eps}%%{FIGURES/Seuils_Re.eps}
$$
\caption{ Thresholds for the onset of acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).}
\label{fig:ThresholdsRe}
\end{figure}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{fig/Omega_beta.eps}
$$
$$
\includegraphics[width=.7\linewidth]{fig/OmegaL_beta.eps}
$$
\caption{ Frequencies corresponding to acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
}
\label{fig:ThresholdsRe}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Linear stability results}

RESULTS : growth rates, eigenmodes, sensitivity,  Comparison with impedance-based predictions. THIS WILL BE DONE FOR $\beta = 1$.

Figure : growth rate / freq. as function of Re

Figure : eigenmodes, adjoint,  sensitivity.

\begin{figure}
\includegraphics[width=\linewidth]{fig/dir_adj_sens.png}
\caption{ Eigenmode, Adjoint and sensitivity}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

\section{Case of a rounded hole}

TO KEEP OR NOT TO KEEP ???

@@

@@

\appendix

\section{Details on complex mapping}

\section{Upstream domain : modelling of a reactive cavity}

THIS IS TO BE KEPT FOR PART III : "augmented incompressible model" to be compared to fully compressible case.

\section{Numerical validations}
Only the mesh and mayle the parameter $L_M$
